О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-09 pps-linear-bound/pps-linear-lower-bound.tex
Intro - first attempt

\section{Introduction.}

>>>>

\section{Introduction.}
Let $\mathbb{N}$ be the set of all positive integers and let $|M_1 - M_2|$ denote the Euclidean distance
between points $M_1$ and $M_2$ in a finite-dimensional space $\mathbb{R}^m$.
An \textit{integral point set} in $m$-dimensional Euclidean space is such a point set $M$ that all the distances between the
points of $M$ are integers and $M$ is not situated on an $(m-1)$-dimensional hyperplane.
Erd\"os and Anning proved~\cite{anning1945integral,erdos1945integral} that every integral point set consists of a finite number of points.
Taking the fact into account, we will denote the set of all integral point sets of $n$ points in $m$-dimensional Euclidean space with
$\mathfrak{M}(m,n)$ (following the notation of~\cite{our-vmmsh-2018}).
The symbol $|M|$ will be used for cardinality of $M$, i.e. the quantity of points in $M$ in our case.

For every finite point set, its diameter is naturally defined as
\begin{equation}
	\operatorname{diam} M = \max_{A,B\in M} |A-B|
	.
\end{equation}
The next emerging question is: how the diameter of an integral point set depends on its cardinality?
One can easily see that every $M\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = h$
can be stretched to $M_p\in\mathfrak{M}(m,n)$ with $\operatorname{diam} M = ph$
for every $p\in\mathbb{N}$.
So, the question above should be rephrased:
how \textit{the least possible} diameter of an integral point set depends on its cardinality?
To answer it, the following function was introduced~\cite{kurz2008bounds,kurz2008minimum}:
\begin{equation}
	d(m,n) = \min_{M\in\mathfrak{M}(m,n)} \operatorname{diam} M = \min_{M\in\mathfrak{M}(m,n)} \max_{A,B\in M} |A-B|
	.
\end{equation}
We also refer to~\cite{kurz2008bounds} for a list of known exact values of $d(m,n)$
and estimations; in the present paper, the case of $m=2$ will mostly be in the focus.

The most significant breakthrough on case of $m=2$ was done by Solymosi~\cite{solymosi2003note},
who proved that $cn \leq d(2,n)$ for a sufficiently small constant $c$.
Followed the details of Solymosi's proof carefully,
one can know out that the inequality holds at least for $c = 1/24$.
The constant was improved in~\cite{our-mz-rus,our-vmmsh-2018}
to $1/8$ for all $n$ and $3/8$ for sufficiently big $n$, respectively.

The paper~\cite{solymosi2003note} contained one more interesting result.
Let us define a function which is ``dual'' to $d(m,n)$ in some sense:
\begin{equation}
	l(m,n) = \min_{M\in\mathfrak{M}(m,n)} \min_{A,B\in M} |A-B|
	.
\end{equation}
Solymosi proved that $l(2,n)\leq 2$.

In the present paper we improve Solymosi's results:
firstly, we obtain a greater constant $c$ in Theorem (TODO: the number of theorem and the exact constant),
using the combined approach with the Point Packing in a Square problem;
then, we prove that $l(m,n)=1$ for all $m$ and $n$ which it is correctly defined on.
